Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-12-01 manuscript/appendix.Rmd
HM comments in appendix
This takes care of everything other than issue #123.

bibliography: library.bib
csl: global-change-biology.csl
nocite: | 
  @hijmans_very_2005; @fick_worldclim_2017; @harris_updated_2014;  @abatzoglou_terraclimate_2018; @trabucco_global_2019

@@

#@hijmans_very_2005; @fick_worldclim_2017; @harris_updated_2014;  @abatzoglou_terraclimate_2018
```
\elandscape
\newpage

\blandscape
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S3 <- read.csv("tables_figures/r2_table1.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S3, format = "latex", booktabs = TRUE, caption = "Table S2. Model form, $\\Delta$AIC, and R$^{2}$ for each climate variable as a single fixed effect in models for each C flux.", caption.short = "Table S2. Model form, $\\Delta$AIC and R$^{2}$ for each climate variable as a single fixed effect in models for each C flux", escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  add_header_above(c(" ", "Latitude"=3, "MAT"=3, "MAP"=3, "T Seas"=3, "P Seas"=3, "ATR"=3, "Solar R"=3, "AI"=3))
```

@@

  knitr::include_graphics("tables_figures/distribution_all_samples.png")
```

\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S2: Scatterplots and Pearson's R values for relationships between latitude and climate variables", out.height='95%', fig.pos='H'}

  knitr::include_graphics("tables_figures/climate_regressions.png")
```
\elandscape

\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S3: Ratios among forest C fluxes as a function of latitude and climate variables.", out.width ='80%', fig.pos='H'}

>>>>

bibliography: library.bib
csl: global-change-biology.csl

@@

```

---
nocite: | 
  @hijmans_very_2005; @fick_worldclim_2017; @harris_updated_2014;  @abatzoglou_terraclimate_2018; @trabucco_global_2019
---

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S3 <- read.csv("tables_figures/r2_table1.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S3, format = "latex", booktabs = TRUE, caption = "Table S2. Model form, $\\Delta$AIC, and R$^{2}$ for each climate variable as a single fixed effect in models for each C flux.", caption.short = "Table S2. Model form, $\\Delta$AIC and R$^{2}$ for each climate variable as a single fixed effect in models for each C flux", escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  add_header_above(c(" ", "Latitude"=3, "MAT"=3, "MAP"=3, "T Seas"=3, "P Seas"=3, "ATR"=3, "Solar R"=3, "AI"=3))
```

@@

  knitr::include_graphics("tables_figures/distribution_all_samples.png")
```
\newpage 
\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S2: Scatterplots and Pearson's R values for relationships among climate variables and latitude", out.height='95%', fig.pos='H'}

  knitr::include_graphics("tables_figures/climate_regressions.png")
```

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S3: Ratios among forest C fluxes as a function of latitude and climate variables.", out.width ='80%', fig.pos='H'}
